MCC Models

### 2019-03-24 papers/full_paper/models.Rmd
kids model predictions and comaprison complete first pass

@@

@@

# model predictions
child_ex3_pragm_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(model = "pragmatic_developmental_noise")%>%
  group_by(model, age,alignment,speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

@@

```{r}
developmental_noise_parameter <- data_frame(
  age = rep(seq(0,2, by = 0.05),1),
  int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41)),
  slope = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41))
) %>%
  mutate(y = plogis(int + slope *age))

ggplot(developmental_noise_parameter, aes(x = age, y= y))+
  geom_line(size = 2)+
  ylab("Noise Parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()
```

@@

@@

@@

@@

```{r plot model predictions ex3 children}
child_model_predictions <- bind_rows(
  child_ex3_pragm_model_predictions_noise,
  child_ex3_pragm_model_predictions_developmental_noise,
  child_ex3_pragm_model_predictions
  #child_ex3_flat_prior_model_predictions,
  #child_ex3_prior_only_model_predictions
  )

@@

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
                     values= c("#859900","#00afaf","#6c71c4","#b58900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","pragmatic_noise","flat_prior","prior_only"),
                     values= c("#859900","#00afaf","#6c71c4","#b58900"))

@@

child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic")%>%
  group_by(model)%>%
  summarise(logP = mean(V1))

@@

child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic_noise")%>%
  group_by(model)%>%
  summarise(logP = mean(V1))

@@

```{r}
child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  chains = 3,
  cores = 3
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic_developmental_noise")%>%
  group_by(model)%>%
  summarise(logP = mean(V1))

@@

@@

child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "flat_prior_noise")%>%
  group_by(model)%>%
  summarise(logP = mean(V1))
```

@@

@@

child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "prior_only_noise")%>%
  group_by(model)%>%
  summarise(logP = mean(V1))
```

@@

child_ex3_model_comparison <- bind_rows(
  child_ex3_pragm_model_likelihood,
 child_ex3_pragm_model_noise_likelihood,
child_ex3_flat_prior_model_noise_likelihood,
  child_ex3_prior_only_model_noise_likelihood
)%>%
  mutate(model = reorder(model,logP))
```

@@

```{r plot model loglikes ex3 children}
ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  ylim(-475,-400)+
  scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
                    values= c("#859900","#00afaf","#b58900","#6c71c4"))

@@

```{r bayes factors ex3 children}
child_ex3_bf <- child_ex3_model_comparison%>%
  spread(model, logP) %>%
  mutate("pragmatic_noise > pragmatic" = pragmatic_noise - pragmatic,
          "pragmatic_noise > flat_prior_noise" = pragmatic_noise - flat_prior_noise,
         "pragmatic_noise > prior_only_noise" = pragmatic_noise - prior_only_noise,
         "flat_prior_noise > prior_only_noise" = flat_prior_noise - prior_only_noise) %>%
  select(-pragmatic,-pragmatic_noise,  -flat_prior_noise, -prior_only_noise)

>>>>

##### Noise parameters

```{r}
ex3_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "pragmatic"),
  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "prior_only"),
  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "flat_prior")
  )

ggplot(ex3_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

##### Noise parameters

```{r}
ex4_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "pragmatic"),
  readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "prior_only"),
  readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "flat_prior")
  )

ggplot(ex4_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

# model predictions
child_ex3_pragm_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
  filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(model = "pragmatic_developmental_noise")%>%
  group_by(model, age,alignment,speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

@@

@@

```{r}
child.ex3.prior.only.predictions.noise <-'

```{r}
# child_ex3_prior_only_model_noise<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions.noise , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
# )%>%
#    saveRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds")

# model predictions
child_ex3_prior_only_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(model = "prior_only_noise")%>%
  group_by(model, age,alignment,speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

## noise parameter
child_ex3_prior_only_model_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```{r}
child.ex3.prior.only.predictions.developmental.noise <-'

```{r}
# child_ex3_prior_only_model_developmental_noise<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.predictions.developmental.noise , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
# )%>%
#    saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds")

# model predictions
child_ex3_prior_only_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
  filter(!(Parameter %in% c("noise_int","noise_slope"))) %>%
  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(model = "prior_only_developmental_noise")%>%
  group_by(model, age,alignment,speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

## noise parameter
child_ex3_prior_only_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

@@

```{r}
child.ex3.flat.prior.predictions.noise <-'

```{r}
child.ex3.flat.prior.predictions.developmental.noise <-'

```{r}
# child_ex3_flat_prior_model_developmental_noise<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.developmental.noise , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
# )%>%
#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds")

# model predictions
child_ex3_flat_prior_model_predictions_developmental_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
  filter(!(Parameter %in% c("noise","noise_int","noise_slope"))) %>%
  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(model = "flat_prior_developmental_noise")%>%
  group_by(model, age,alignment,speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

## noise parameter
child_ex3_flat_prior_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

```{r}
# child_ex3_flat_prior_model_noise<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.predictions.noise , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
# )%>%
#    saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds")

# model predictions
child_ex3_flat_prior_model_predictions_noise <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(!(Parameter %in% c("noise"))) %>%
  separate(Parameter, into = c("age", "speaker", "alignment"), sep="/")%>%
  mutate(model = "flat_prior_noise")%>%
  group_by(model, age,alignment,speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

## noise parameter
child_ex3_flat_prior_model_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

@@

### Noise parameters

```{r}
child_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "pragmatic"),
  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "prior_only"),
  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(model = "flat_prior")
  )

ggplot(child_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

### Developmental noise parameters
```{r}
developmental_noise_parameter <- data_frame(
  age = rep(seq(0,2, by = 0.05),3),
  model = c(rep("pragmatic",41),
            rep("flat_prior",41),
            rep("prior_only",41)),
  int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41),
          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41),
          rep(child_ex3_prior_only_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41)
          ),
  slope = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41),
          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41),
          rep(child_ex3_prior_only_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41))
) %>%
  mutate(y = plogis(int + slope *age))

ggplot(developmental_noise_parameter, aes(x = age, y= y, col = model))+
  geom_line(size = 1)+
  ylab("Noise parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

```{r plot model predictions ex3 children}
child_model_predictions <- bind_rows(
  child_ex3_pragm_model_predictions_noise,
  #child_ex3_pragm_model_predictions_developmental_noise,
  child_ex3_pragm_model_predictions,
  child_ex3_prior_only_model_predictions_noise,
  child_ex3_flat_prior_model_predictions_noise
  #child_ex3_flat_prior_model_predictions,
  #child_ex3_prior_only_model_predictions
  )

@@

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 2,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
                     values= c("#b58900","#00afaf","#6c71c4","#859900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
                     values= c("#b58900","#00afaf","#6c71c4","#859900"))

@@

child_ex3_pragm_model_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic",
         parameter = "parameter free")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

child_ex3_pragm_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic",
         parameter = "noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

```{r}
# child_ex3_pragm_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

child_ex3_pragm_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "pragmatic",
         parameter = "developmental noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

```{r}
child.ex3.flat.prior.marginal.likelihood <-'

```{r}
# child_ex3_flat_prior_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

child_ex3_flat_prior_model_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "flat_prior",
         parameter = "parameter free")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

@@

child_ex3_flat_prior_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "flat_prior",
         parameter = "noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

```{r}
child.ex3.flat.prior.developmental.noise.marginal.likelihood <-'

```{r}
# child_ex3_flat_prior_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

child_ex3_flat_prior_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "flat_prior",
         parameter = "developmental noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))

@@

```{r}
child.ex3.prior.only.marginal.likelihood <-'

```{r}
# child_ex3_prior_only_model_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

child_ex3_prior_only_model_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "prior_only",
         parameter = "parameter free")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

@@

child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "prior_only",
         parameter = "noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

```{r}
child.ex3.prior.only.developmental.noise.marginal.likelihood <-'

```{r}
# child_ex3_prior_only_model_developmental_noise_likelihood<- webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   chains = 3,
#   cores = 3
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

child_ex3_prior_only_model_developmental_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")%>%
  as.tibble()%>%
  mutate(model = "prior_only",
         parameter = "developmental noise")%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(V1))
```

@@

child_ex3_model_comparison <- bind_rows(
  child_ex3_pragm_model_likelihood,
  child_ex3_pragm_model_noise_likelihood,
  child_ex3_pragm_model_developmental_noise_likelihood,
  child_ex3_flat_prior_model_noise_likelihood,
  child_ex3_flat_prior_model_likelihood,
  child_ex3_flat_prior_model_developmental_noise_likelihood,
  child_ex3_prior_only_model_noise_likelihood,
  child_ex3_prior_only_model_likelihood,
  child_ex3_prior_only_model_developmental_noise_likelihood
)%>%
  ungroup()%>%
  mutate(model = reorder(model,logP))
```

@@

```{r plot model loglikes ex3 children}
ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  facet_grid(~parameter)+
  ylim(-475,-400)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))

@@

```{r bayes factors ex3 children}
child_ex3_bf <- child_ex3_model_comparison%>%
  group_by(parameter)%>%
  spread(model, logP) %>%
  mutate("pragmatic > flat_prior" = pragmatic - flat_prior,
         "pragmatic > prior_only" = pragmatic - prior_only,
         "flat_prior > prior_only" = flat_prior - prior_only) %>%
  select(-pragmatic,-flat_prior, -prior_only)
